%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Pixel Table} % Organization
    {Cryptocurrency Investment Simulation Engine} % Project title
    {Denver, CO} % Location
    {} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created an open source cryptocurrency trading engine using Go.}
        \item {Enabled the ability to run trading algorithms against historical data for 100+ trading pairs.}
        \item {Implemented Goroutines to enable simulation concurrency.}
        \item {Used Websockets to transfer data between a web client and trading engine.}
        \item {Wrote a modern UI using Angular and Angular Material.}
    \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
    \cventry
    {Pratt \& Miller Engineering} % Organization
    {High Performance Racing CMS} % Project title
    {Huntersville, NC} % Location
    {} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked alongside engineers at professional automotive companies to design tools used in performance and optimization testing of vehicles.}
        \item {Created Angular services \& components which processed large amounts of historical and real-time data from a .Net Core backend.}
        \item {Utilized RxJs to process data streams and lazy load data within components.}
        \item {Implemented state management techniques using NGXS.}
    \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
    \cventry
    {T4S Partners} % Organization
    {Big Four Financial Application} % Project title
    {Denver, CO} % Location
    {} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of developers to create and deliver highly customized application functionality.}
        \item {Implemented the architectural design and creation for an enterprise Angular web application.}
        \item {Configured an Azure pipeline for continuous deployment and integration across environments.}
        \item {Created a mono-repo using Nx which allows for optimal code re-use and faster deployments.}
        \item {Wrote a full end-to-end test suite using Cypress.}
        \item {Closely worked with a .NET Core back-end team to consume multiple APIs and create a mock HTTP environment for local testing.}
        \item {Collaborated with business and UX teams to design an application with a modern look and feel.}
    \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
    \cventry
    {Charter Communications} % Organization
    {Spectrum Client Portal} % Project title
    {Denver, CO} % Location
    {} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinated with software architects and UX teams to design scalable web applications used by thousands of customers.}
        \item {Optimized the performance of Angular web applications by implementing various design patterns.}
        \item {Created sharable components to be used across multiple internal teams via a mono repository.}
        \item {Conducted multiple technical interviews for new job candidates.}
    \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
    \cventry
    {Optum Technology} % Organization
    {CRM \& Site Builder} % Project title
    {Eden Prairie, MN} % Location
    {} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led and participated in development team efforts of a new app store using Angular and TypeScript.}
        \item {Implemented single sign-on user authentication for multiple web applications.}
        \item {Developed multiple RESTful APIs in Groovy using Java Spring, MySQL, and Liquibase.}
        \item {Configured AWS CloudFront distributions, DNS entries, and RDS instances.}
        \item {Designed and maintained a Jenkins deployment pipeline.}
    \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
    \cventry
    {Reiser Relief} % Organization
    {Website Administrator} % Project title
    {Minneapolis, MN} % Location
    {} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Volunteered to single-handedly design, create, and manage reiserrelief.org.}
        \item {Developed an open source website used by thousands annually.}
        \item {Created a donation platform using Stripe.}
        \item {Generated a static site using Angular Universal.}
        \item {Created an administrative portal using Firebase and Angular.}
    \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
